---
title: "Day One: Introductions"
subtitle: "SDS 237: Data Ethnography"
author: |
  Lindsay Poirier<br/>
  <span style = 'font-size: 70%;'>
  [Statistical & Data Sciences](http://www.smith.edu/sds), Smith College<br/>
  </span>
date: |
  Fall 2022<br/>
  `r sds::img_logo(width = 64)`
output:
  sds::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE}
# sds::duo_smith()
sds::mono_light_smith()
```


class: center, middle
# Statistical & Data Sciences
---
# What is ethnography?

.pull-left[

* study of human culture and social relations
* involves interactions and observations, recording, and analysis
* data collection methods are predominantly qualitiatve 
* analysis is predominantly *inductive* and *interpretive*
]

.pull-right[

![](https://upload.wikimedia.org/wikipedia/commons/7/75/Inductive_Deductive_Reasoning.svg)
Brian Brondel at English Wikibooks, CC BY-SA 2.5 <https://creativecommons.org/licenses/by-sa/2.5>, via Wikimedia Commons

]

---

class: center, middle
# What is data?

---

# What is data ethnography?

* 

---

# What fields of research inform data ethnography?

* Science and Technology Studies (STS)
  * an interdisciplinary field that examines how science, technology, politics, and culture all co-produce each other
  * STS disciplines include anthropology, sociology, literary studies, political science, economics, and more
  * What might be some examples?
* Critical Data Studies
  * an interdisciplinary field examining the epistemological, political, social, and ethical aspects of data artifacts, practices, and infrastructures
  * What are some political dimensions of data? Examples?
  * What are some ethical dimensions of data? Examples?
  * Is there a difference?
  
---

class: center, middle
# What is the professor?
  
---


# Exercise

.pull-left[

<iframe width="512" height="332" src="https://player.pbs.org/viralplayer/2365415341/" allowfullscreen allow="encrypted-media" style="border: 0;"></iframe>

]

.pull-right[

* Ethnographers often collect more data than they know what to do with
* Write as much as possible about:
  * what people do/why they do it
  * beliefs/values/expertise
  * social structures
  * questions you are left with
  
]
